Discussion Draft

### 2020-03-17 doc/Discussion.rmd
more notes and edits

@@

@@

# INTERFERENCE evolution

@@

1. Cattle (Ma?), when comparisons of genetic map length and interference strength are made across strengths within sex, the strain with the higher genome wide recombinaiton rate also has stronger interference (measured as nu gamma parameter)

@@

@@

>>>>

```{r Evolve.tratis.outline, include=FALSE}

@@

```{r evo.DSB, include=FALSE}

@@

# evolution in Interference

```{r evo.interference, include=FALSE}

#review results,

#why unexpected

#assuptions for predictions

#models that predict this pattern?

@@

1. Cattle (Ma?) [@ma2015cattle] ? (or newer one), when comparisons of genetic map length and interference strength are made across strengths within sex, the strain with the higher genome wide recombinaiton rate also has stronger interference (measured as nu gamma parameter)

@@

```{r Model.testing, echo=FALSE}

@@

```{r Spindle.Model, include=FALSE}

#1. context of meiosis

#2. 
```
